%%%%%%%%%%%%%%%%%%%%%%%%%
% Chapter: Introduction %
%%%%%%%%%%%%%%%%%%%%%%%%%
The work presented in this thesis introduces and evaluates a novel approach for
the open corpus problem in intelligent tutoring systems, which is especially
applicable to the usage of Open Educational Resources.
In its core, the developed system applies genetic algorithms to construct
sequences of learning material based on the measured learning gain it caused,
while balancing exploration and exploitation using Upper Confidence Bound (UCB)
selection.

%Explain intelligent tutoring systems
%Often targeted problem is personalization
%Explain the open corpus problem
%Discuss rise of Open Educational Resources
%New problem, not all content is good or applicable. A lot is not known about
%it.

\section{Problem statement}
% Open Education is a trend
There is a growing number of open educational resources (OERs) available for
teachers around the world to reuse in their own learning modules.

% There is a problem with the growing number of OER
With this increasing number of open education resources come various
difficulties for teachers to find resources that
are relevant for their educational purposes \citep{Ochoa2011}. Additionaly it
becomes more dificult to ensure the quality of these OERs \citep{Cechinel2011}.
Work has been done on improving the search of OERs, for an overview see
\citep{Ochoa2008}. All of these attempts however focus on the metadata provided
with the OER. The assumption in this research appears to be that when an OER is
relevant (i.e.: contains the right keywords and contextual information in the
metadata), the OER is highly likely to be useful in a course. Teachers that
search OERs get presented a list of ranked OERs based on their relevance score.
This means, that it is left to the teacher to go through this list and select
the OER that suits the students best. An activity that is going to be more
time-intensive with the increasing number of relevant OERs. Furthermore whether
an OER is suitable for a student also depends on the OER’s effectiveness in
increasing the student’s compentences, something which is not trivial for a
teacher to predict. On top of that, students don't all learn in the same way or
have the same prior knowledge.

% Personalization is a trend, but not taking into account learning evidence
The latter has also motivated various scientific communities to create more
personalized learning experiences by means of technology. These communities
include Intelligent Tuturing Systems, Adaptive Hypermedia Systems and Learning
Analytics. A big part of the personalized learning experience comes down to
connecting the learner with a new educational resource that is, according to
some metric, the best next step for the learner to take. There are usually two
flavors in the presentation of this new connection, either by automatic
redirection in adaptive systems or by a list of recommendations. Either way, a
system must first be able to find educational resources that are useful, by
some notion, for a learner. Within the educational domain such recommendations
are often based on a viewing history of learners that are somehow similar to
the target learner. In some systems a more direct learner feedback is used in
the shape of likes or ratings. In a sense these systems are all variations on
the classic shopping case where products are recommended to a customer based on
the purchases of similar customers. However, whether a learner visited or liked
a certain educational resource (for whatever reason) is a rather indirect way
to determine the effectiveness of that resource in learning the student
something new.

% We should try to take effectiveness into account
Both the world of open educational resources and the world of personalized
learning experiences could benefit greatly of being able to automatically take
the effectiveness of an educational resource into account. If OERs could
automatically be rated on effectiveness for a specific student or student type
it would first of all make it a lot easier for teachers to select material out
of the large repository. Second of all it would open up the possibility to
automatically find, mark and potentially even remove OERs that are always less
effective than other comparable OERs. For personalized education it would mean
that recommendations could be made baded on emperical evidence that the
recommendation is likely to be succesful. The benefit is amplified when the two
worlds combine. It is to be expected that virtual learning environments will at
some point be connected to large online repositories of OERs instead of being
limited to offer only the teacher’s hand-picked resources. Which is even more
vital when there is not a clear teacher role, which is often the case in
life-long learning and sometimes also in corperate training settings.

% Learning objects are not independant when it comes to effectiveness

%This is however only possible when the learning environment is autonomously
%capable of picking the right resources for a student, since otherwise it will
%almost certainly reduce the quality of the
%learning experience. This step becomes even more urgent with the increase of
%massive open online courses (MOOCs), which contain enormous amounts of students
%that spend most of their learning activites within the virtual learning
%environments.

\section{Curriculum Sequencing}
\label{sec:task_curr_seq}
\begin{itemize}
	\item Introduce curriculum sequencing. This is problem is part of the
		broader field of curriculum sequencing problems.
		\begin{itemize}
			\item generate personalized learning path through content (cite
				brusilovsky)
			\item old feature, recent necessity due to hyperspace. OER
				especially!
		\end{itemize}
	\item Typically fitting content to students, due to differences in student
		ability or learning style. OER adds a challenge of also dealing with
		bad content.
	\item Furthermore several examples of curriculum sequencing in the
		literature that apply evolutionary computing focus on creating a
		content sequencing with a smooth built-up in dificulty. However, in OER
		this difficulty is not necessarily known. And if it is, there is no
		guarantee that it will be correct.
	\item Slightly different from curriculum generation, where the sequence of
		material is generated one step at a time as the students progresses.
		Curriculum sequencing decides on the entire sequence at the beginning.
\end{itemize}

\section{Background}
\subsection{Open Educational Resources}
\begin{itemize}
	\item What are open educational resources?
	\item What makes OER different from other sources of educational material
	\item What are the challenges?
\end{itemize}
% there is not that much known about every OER. It costs authors often too much effort, or are otherwise not able, to supply sufficient meta records.
%TODO: References!
\subsubsection{Meta data}

\subsection{Genetic Algorithms}
